\LARGE \bf How Children Perceive and Interact with a Robot that Behaves Unexpectedly -- The Domino Experiment

### 2014-09-29 paper.tex
Formatting: down to 8.75 pages

\begin{figure}[ht!] 
    \centering 
    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
    \caption{\small The study took place in one of the rooms in the lab. One
    child is located in a tent (referred to as \textit{the receiver}), while the
    other (referred to as \textit{the searcher}) is asked to sit on one of the
    three beanbags, behind which each 3 domino tiles are distributed (displayed
    as black stars). A playground with a river drawn on it is used as an
    imaginary barrier that only the robot is allowed to cross. The solid green
    arrows, show the robot's path for the \textit{correct} behaviour. The blue
    dashed arrow visualizes a possible \textit{lost} path, where the Ranger
    stops and remains at a wrong stop (denoted by the blue cross). The yellow
    arrows reflect a possible \textit{mistake} path, where the robot goes wrong
    but then turns back and goes to the searcher child. The red dashed arrow
    visualizes a possible \textit{disobey} path where the robot goes wrong, then
    turns toward the child but remains at the wrong stop (red cross).}

@@

We annotated children's behaviour in the video records, and coded 10 different
actions:

    \item \textbf{Explore}: when children actively try to find out what the
        robot is doing (\eg by looking under the box); attentively watch or
        observe the robot (\eg attentively waiting for the box to show a
        reaction); experiment with the robot to figure out how it works (\eg put
        hands in front or inside of the box to see what happens);

    \item \textbf{Misuse}: when children kick the robot, poke it in its
        ``eye'', try to climb on or inside the box, drive / push the robot
        around, stop the robot's wheels with a foot;

    \item \textbf{Put domino}: when a domino tile is put inside the box;

    \item \textbf{Remove domino (rem)}: when a domino tile is removed from the
        box;

    \item \textbf{Gesture}: when gestures are used to communicate /
        interact with the robot (\eg pointing gestures, waving at the robot);

    \item \textbf{Touch}: when the box is touched (\eg petted or
        caressed);

    \item \textbf{Show}: when a child shows something to the robot (\eg
        by holding a domino tile in front of its eyes);

    \item \textbf{Call}: when a child calls the robot to come over;

    \item \textbf{Talk}: when a child directly talks to the robot (using
        direct speech) besides calling the robot;

    \item \textbf{Look}: when a child looks at the experimenter due to
        confusion caused by the robot; look is not coded when the experimenter
        asks a question to the child;

@@

\begin{table}[h!t]
\centering
\footnotesize
\begin{tabular}{p{0.9\linewidth}}
    \toprule
    \textbf{Expectations} \\
    \midrule

@@

\textbf{Perception: \textit{(max. 13 points)}}
\begin{itemize}
	\item Ascribe \textbf{mental states / feelings} to Ranger: \textit{0-4 points}\\
	(2 points for agreeing that Ranger can be happy or sad; 2 points for attributing Ranger with hunger or tiredness)
	\item Ascribe \textbf{cognitive abilities / intention} to Ranger: \textit{0-4 points}\\ 
	(each 0.5 points for ascribing seeing and hearing ability; 1 point for agreeing that Ranger can go out the door by itself; 1 point for disagreeing that Ranger always obeys; 1 point for agreeing that Ranger can do something silly)
	\item Ascribe \textbf{sociality / companionship} to Ranger: \textit{1 point}\\ 
	(1 point for agreeing that Ranger can be a friend)
	\item Ascribe \textbf{moral standing} to Ranger: \textit{1 point}\\ (1 point for disagreeing that Ranger be left alone at home)
	\item Other \textbf{anthropomorphic statements}: \textit{0-3 points}\\ 
	(1 point for anthropomorphic reason for Ranger's misbehaviour; 2 points for anthropomorphic reason for not leaving Ranger alone) 
\end{itemize}

\textbf{behaviour: \textit{(max. 3 points)}}
\begin{itemize}
	\item Use of \textbf{direct speech} toward Ranger: \textit{1 point}\\
	(\textit{calling} the robot to come over is not considered)
	\item Use of \textbf{polite formulations} toward Ranger: \textit{1 point}\\ 
	(\eg saying \textit{``thank you Ranger''} or \textit{``please Ranger ...''} or \textit{``goodbye''})
	\item Use of \textbf{social or pointing gestures} toward Ranger: \textit{1 point}\\ 
	(\eg waving at the robot, nodding)
\end{itemize}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=1.0\linewidth]{domino-why-misbehavior.pdf}   
    \caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible
    to the question why the robot did not come over, and we received 37 answers.
    This question shows that children did not necessarily interpret the misbehaviour
    in the way we had assumed.}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\linewidth]{domino-intention.pdf}
    \caption{\small \textbf{Attribution of intention to Ranger.} Children were
        asked these questions at both interviews. Concerning question (a), there
        are no remarkable differences in children's responses given in the
        \textit{first} and \textit{second} interview.  Children tend to think
        Ranger does always obey to them, even after it misbehaved. There is
        however a small difference in the responses to question (b).  After the
        robot misbehaved, 8 children think the robot could do something silly whereas
        first, only 3 children answered like this.}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\columnwidth]{domino-correlation.pdf}

>>>>

\begin{figure}[ht!] 
    \centering 
    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
    \caption{\small \textbf{Experimental setting} One child is located in a
        tent, while the other is asked to sit on one of the three beanbags,
        behind each of which 3 domino tiles are distributed (displayed as black
        stars). A playground with a river drawn on it is used as an imaginary
        barrier that only the robot is allowed to cross. The solid green arrows
        show the robot's path for the \textit{correct} behaviour. The blue
        dashed arrow visualizes a possible \textit{lost} path, where the Ranger
        stops and remains at a wrong stop. The yellow arrows reflect a possible
        \textit{mistake} path, where the robot goes wrong but then turns back
        and goes to the child. The red dashed arrow visualizes a possible
        \textit{disobey} path where the robot goes wrong, then turns toward the
        child but stays at a wrong position.}

@@

We annotated children's behaviour in the video records, and coded 10 different
actions: \textbf{explore} (actively try to find out what the robot is doing, \eg
by looking under the box; attentively watch or observe the robot; experiment
with the robot to figure out how it works); \textbf{misuse} (kick the robot,
poke it in its ``eye'', try to climb on or inside the box, drive/push the robot
around, stop the robot's wheels with a foot); \textbf{put} (a domino tile is put
inside the box); \textbf{remove} (a domino tile is removed from the box);
\textbf{gesture} (gestures are used to communicate/interact with the robot, \eg
pointing gestures, waving at the robot); \textbf{touch} (the box is touched, \eg
petted or caressed); \textbf{show} (show something to the robot; \textbf{call}
(call the robot to come over); \textbf{talk} (all the other case of direct
verbal interaction); \textbf{look} (when a child looks \emph{at the
experimenter} due to confusion caused by the robot; look is not coded when the
experimenter asks a question to the child);

@@

\begin{table}[h!t]
\centering
\footnotesize
\begin{tabular}{p{1\linewidth}}
    \toprule
    \textbf{Expectations} \\
    \midrule

@@

\textbf{Perception}: \textit{(max. 13 points)}

\begin{itemize}
    \item Ascription of \textbf{mental states / feelings}: \textit{2 points} for agreeing
            that Ranger can be happy or sad; \textit{2 points} for attributing Ranger with
        hunger or tiredness.

    \item Ascription of \textbf{cognitive abilities / intention}: each \textit{0.5
        points} for ascribing seeing and hearing ability; \textit{1 point} for agreeing
            that Ranger can go out the door by itself; \textit{1 point} for disagreeing that
            Ranger always obeys; \textit{1 point} for agreeing that Ranger can do something
        silly.

    \item Ascription of \textbf{sociality / companionship}: \textit{1 point} for agreeing
        that Ranger can be a friend.

    \item Ascription of \textbf{moral standing}: \textit{1 point} for disagreeing that
        Ranger be left alone at home.

    \item Other \textbf{anthropomorphic statements}: \textit{1 point} for anthropomorphic
        reason for Ranger's misbehaviour; \textit{2 points} for anthropomorphic reason
        for not leaving Ranger alone.

\textbf{Behaviour}: \textit{(max. 3 points)}
\begin{itemize}
    \item Use of \textbf{direct speech}: \textit{1 point} (not considering
        \textit{calling} the robot to come over).

    \item Use of \textbf{polite formulations}: \textit{1 point} (\eg
        \textit{``thank you Ranger''} or \textit{``please Ranger ...''}).

    \item Use of \textbf{social or pointing gestures}: \textit{1 point} (\eg
        waving at the robot).

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.8\linewidth]{domino-why-misbehavior.pdf}   
    \caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible
    to the question why the robot did not come over, and we received 37 answers.
    This question shows that children did not necessarily interpret the misbehaviour
    in the way we had assumed.}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\linewidth]{domino-intention.pdf}
    \caption{\small \textbf{Attribution of intention to Ranger.} Children were
        asked these questions at both interviews. Concerning question (a), there
        are no remarkable differences in children's responses given in the
        \textit{first} and \textit{second} interview.  Children tend to think
        Ranger does always obey to them, even after it misbehaved. There is
        however a small difference in the responses to question (b).  After the
        robot misbehaved, 8 children think the robot could do something silly whereas
        first, only 3 children answered like this.}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\columnwidth]{domino-correlation.pdf}
